---
title: "P9"
author: "Steph Bossert"
date: "5/11/2021"
output: html_document
---

```{r data and packages}
library(tidyverse) 
library(tidymodels)
library(viridis)
library(openintro)
library(haven)
library(haven)
HW1_data_copy <- read_sav("~/Desktop/HW1_data copy.sav")
View(HW1_data_copy)
HW1_data<- HW1_data_copy
```


#We are going to do a homework problem set but through R (originally ran through SPSS)
```{r data}
view(HW1_data)
#8 variables GPA and IQ as well as motivation level
```



#Run sinple regression- predict GPA from IQ
```{r regression}
m_IQ=lm(GPA~IQ, data = HW1_data) #Create the linear regression
summary(m_IQ)

H = HW1_data; plot( H$IQ, H$GPA )
lmSimple <- lm( GPA ~ IQ, data = HW1_data )
abline( lmSimple )

#plot
ggplot(HW1_data, aes(x=IQ, y=GPA)) + 
  geom_point(shape=18, color="blue")+
  geom_smooth(method=lm, se=FALSE, linetype="solid",
             color="white")
```


#interpret results: IQ accounts for 2.1% of variance in GPA

#Multiple regression
```{r mr}
linear_reg() %>%
 set_engine("lm") %>%
  fit(GPA ~ IQ + Mot, data = HW1_data) %>%
  tidy()
```

#Interpret: MOT account for much more of the variance in GPA than IQ does. If two people have the same IQ, a one point increase in MOT is assocaited with a .87 increase in GPA. 

###Write the model:
# -1.75 + .007(IQ) + .87(Mot)




